A geometric approach to linear and quadratic Chabauty

### 2020-01-27 MS.tex
Added TODO for formal groups

\newcommand{\den}{\mathop{\mathgroup\symoperators den}\nolimits}
\newcommand{\ggd}{\mathop{\mathgroup\symoperators ggd}\nolimits}
\newcommand{\des}{\text{d.e.s.d.a.\ }}
%\newcommand{\opg}{\text{d.e.s.d.a.\ }}
\newcommand{\blokje}{\hfill $\Box$\\}
%Om je bewijs of je antwoord af te sluiten.
\newcommand{\header}[1]{\vspace{0.5cm}\framebox[\linewidth]{\textsc{Exercise #1}}\\}
\newcommand{\deel}[1]{\textbf{#1)}\ }
\newcommand{\macht}[1]{\mathcal{P}(#1)}
\newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Lcal}{\mathcal{L}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\NP}{\mathcal{NP}}
\newcommand{\NPC}{\mathcal{NPC}}
\newcommand{\F}{\mathbb{F}}
\renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
\newcommand{\rad}{\text{rad}}
\newcommand{\x}{x}
\newcommand{\tensor}{\otimes}
\newcommand{\Ring}{\textbf{Rings}}
\newcommand{\Sets}{\textbf{Sets}}

@@

Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, we can look at the completion along the zero section $\Hat{O}_{G,e}$. By smoothness, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$. This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.

@@

>>>>

\newcommand{\den}{\mathop{\mathgroup\symoperators den}\nolimits}
\newcommand{\ggd}{\mathop{\mathgroup\symoperators ggd}\nolimits}
\newcommand{\des}{\text{d.e.s.d.a.\ }}
%\newcommand{\opg}{\text{d.e.s.d.a.\ }}
\newcommand{\blokje}{\hfill $\Box$\\}
%Om je bewijs of je antwoord af te sluiten.
\newcommand{\header}[1]{\vspace{0.5cm}\framebox[\linewidth]{\textsc{Exercise #1}}\\}
\newcommand{\deel}[1]{\textbf{#1)}\ }
\newcommand{\macht}[1]{\mathcal{P}(#1)}
\newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\G}{\mathbb{G}}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Lcal}{\mathcal{L}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\NP}{\mathcal{NP}}
\newcommand{\NPC}{\mathcal{NPC}}
\newcommand{\F}{\mathbb{F}}
\renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
\newcommand{\rad}{\text{rad}}
\newcommand{\x}{x}
\newcommand{\tensor}{\otimes}
\newcommand{\Ring}{\textbf{Rings}}
\newcommand{\Sets}{\textbf{Sets}}

@@

Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, we can look at the completion along the zero section $\Hat{O}_{G,e}$. By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$. This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.

@@

TODO: explain that the formal group gives the group law on $J(\Z_p)_0$. Explain the logarithm. Prove Theorem~\ref{thm:kappanice}.
